quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.Rmd
Figure out how to handle reference with htmltool object

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)
library(plotly)
library(crosstalk)
#library(tools)

@@

This paper presents the R package, `quollr`, which is useful for understanding how NLDR warps high-dimensional space and fits the data.

@@

```{r, eval=knitr::is_html_output(), fig.cap="algorithm"}

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr;",
                   hex_grid_scurve_int,
                    htmltools::div(
                      style = "margin-top: 13px;",  # adjust px as needed
                      scurve_umap_model_vis
                    )),
    device = "xs"
  )
```

>>>>

```{r load-libraries}
library(quollr)
library(tibble)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(patchwork)
library(readr)
library(plotly)
library(crosstalk)
library(htmltools)
#library(tools)

@@

This paper presents the R package, `quollr`, which is useful for understanding how NLDR warps high-dimensional space and fits the data ([Figure 1](#fig-algo)).

@@

htmltools::browsable(
  tagList(
    tags$div(
      id = "fig-algo",  # This is the anchor
      crosstalk::bscols(
        htmltools::div(
          style = "display: grid; grid-template-columns: 1fr 1fr;",
          hex_grid_scurve_int,
          htmltools::div(style = "margin-top: 13px;", scurve_umap_model_vis)
        ),
        device = "xs"
      ),
      tags$p(tags$strong("Figure 1:"), " Algorithm to visualize the 2D model.")
    )
  )
)

### 2025-05-19 paper-quollr.tex
Figure out how to handle reference with htmltool object

This paper presents the R package, \texttt{quollr}, which is useful for understanding how NLDR warps high-dimensional space and fits the data.

>>>>

This paper presents the R package, \texttt{quollr}, which is useful for understanding how NLDR warps high-dimensional space and fits the data (\hyperref[fig-algo]{Figure 1}).
